### 2017-04-04 paper/oopsla17-submission/learning.tex
some decision tree text

\paragraph{Decision Trees}
\ES{TODO: Maybe Huma?}

>>>>

\paragraph{Decision Trees}
Decision tree algorithms learn a tree of binary predicates over the
features, recursively partitioning the input space until a final
classification can be made.
%
Each node in the tree contains a single predicate of the form
$x_j \leq t$ for some threshold $t$, which determines whether a given
input should proceed down the left or right subtree.
%
Each leaf is labeled with a prediction and the fraction of training
samples that would reach it, the latter quantity can be interpreted as
the decision tree's confidence in its prediction.
\ES{HUMA: is this correct?}

Training a decision tree entails finding both a set of good partitioning
predicates and a good ordering of the predicates.
%
This is usually done in a top-down greedy manner by selecting the
predicate the best partitions the entire training set, and recursively
partitioning the subsets.
%
Standard algorithms for training decision trees include C4.5 \ES{CITE} and
CART \ES{CITE}.
%
Overfitting can also be a problem for decision trees; the countermeasure
is usually either halting the learning process before the tree grows too
deep, or pruning the resulting tree.

The advantages of decision trees are that they are relatively easy to
train and that they produce a \emph{white-box} model, making it trivial
to analyze the entire model and explain individual predictions.
%
The disadvantages are that they are prone to overfitting and that the
model can be unstable, \ie small changes to the training data may
produce large changes in the model.
%
Both disadvantages are addressed by random forests.
